---
title: "Campaign Impact Analysis"
subtitle: "Prepared for the Head of Marketing"
format:
  html:
    theme: flatly
    mainfont: "-apple-system, BlinkMacSystemFont, 'Segoe UI', Helvetica, Arial, sans-serif"
    toc: true
    toc-depth: 2
    embed-resources: true
    fig-width: 7
    fig-height: 3.4
execute:
  echo: false
  warning: false
params:
  outcome: "visit"
  arm: "Mens E-Mail"
---

```{r setup}
library(ggplot2)
library(knitr)

# Quarto evaluates chunks in an environment created by rmarkdown::render(),
# not the global environment. Sourcing into knit_global() puts the analysis
# functions in the same environment they are called from.
root <- rprojroot::find_root(rprojroot::has_file("config.yml"))
for (f in list.files(file.path(root, "R"), pattern = "[.][Rr]$", full.names = TRUE)) {
  source(f, local = knitr::knit_global())
}

cfg <- config::get(file = file.path(root, "config.yml"))
cfg$data$path <- file.path(root, cfg$data$path)

res <- build_results(cfg, outcome = params$outcome, arm = params$arm)
```

## Summary

```{r}
#| output: asis
cat(paste0("- ", results_headlines(res), collapse = "\n"))
```

## What was analysed

```{r}
m <- res$meta
kable(data.frame(
  Field = c("Observations", "Groups", "Control group", "Outcome",
            "Covariates considered", "Significance level", "Multiple-comparison correction",
            "Source", "Generated"),
  Value = c(format(m$n, big.mark = ","),
            paste(sprintf("%s (%s)", m$arms, format(m$n_by_arm, big.mark = ",")), collapse = "; "),
            m$control, m$outcome,
            paste(m$covariates, collapse = ", "),
            m$alpha, m$correction,
            basename(m$source), m$generated),
  check.names = FALSE))
```

## Method selected

**`r res$diagnosis$designs[[res$diagnosis$recommended]]$label`**

`r res$diagnosis$rationale`

```{r}
d <- res$diagnosis
kable(data.frame(
  Design = vapply(d$designs, `[[`, character(1), "label"),
  Supported = ifelse(vapply(d$designs, `[[`, logical(1), "supported"), "yes", "no"),
  Reason = vapply(d$designs, `[[`, character(1), "reason"),
  check.names = FALSE, row.names = NULL))
```

## Effect estimates

```{r}
e <- res$experiment$estimates
kable(data.frame(
  Arm = e$arm,
  Estimate = sprintf("%.4f", e$estimate),
  `95% CI` = sprintf("%.4f – %.4f", e$ci_low, e$ci_high),
  `Relative lift` = ifelse(is.na(e$rel_lift), "—", sprintf("%+.1f%%", 100 * e$rel_lift)),
  `p (adjusted)` = ifelse(e$p_adjusted < 1e-4, "<0.0001", sprintf("%.4f", e$p_adjusted)),
  `Detection floor (MDE)` = sprintf("%.4f", e$mde),
  check.names = FALSE))
```

```{r}
ggplot(e, aes(x = estimate, y = arm)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey55") +
  geom_errorbarh(aes(xmin = ci_low, xmax = ci_high), height = 0.12, linewidth = 0.6) +
  geom_point(size = 3, colour = "#2c7fb8") +
  labs(x = paste("Effect on", res$meta$outcome), y = NULL) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank())
```

The detection floor is the smallest effect this design could reliably identify. An estimate close to that floor is statistically detectable but its magnitude is imprecisely measured — worth noting before budgeting against it.

```{r}
#| output: asis
if (!is.null(res$bayes)) {
  p <- res$bayes$posteriors
  cat("### Probability readout\n\n")
  print(kable(data.frame(
    Arm = p$arm,
    `Probability it beats control` = sprintf("%.3f", p$prob_beats_control),
    `Median difference` = sprintf("%.4f", p$diff_median),
    `95% credible interval` = sprintf("%.4f – %.4f", p$diff_low, p$diff_high),
    check.names = FALSE)))
  cat(sprintf("\n\n%s prior, %s draws, seed %d.\n",
              res$bayes$meta$prior,
              format(res$bayes$meta$draws, big.mark = ","),
              res$bayes$meta$seed))
}
```

## Assumptions checked

```{r}
kable(data.frame(
  Check = vapply(res$checks, `[[`, character(1), "label"),
  Status = vapply(res$checks, `[[`, character(1), "status"),
  Finding = vapply(res$checks, `[[`, character(1), "message"),
  check.names = FALSE, row.names = NULL))
```

## How much can an unadjusted comparison mislead?

```{r}
#| output: asis
bmeta <- res$benchmark$meta
cat(sprintf(
  "The randomised data gives a known true effect. A biased subsample of %s observations was then drawn where retention depends on %s, deliberately breaking the random assignment. Each estimator was run on that subsample and scored against the truth.\n\nThis sample is constructed, not observed. It exists to test whether the adjustment methods recover an answer that is already known.\n",
  format(bmeta$n_confounded, big.mark = ","),
  paste(names(bmeta$construction$drivers), collapse = " and ")))
```

```{r}
b <- res$benchmark$benchmark
kable(data.frame(
  Estimator = b$estimator,
  Estimate = sprintf("%.4f", b$estimate),
  `True effect` = sprintf("%.4f", b$truth),
  Error = sprintf("%+.1f%%", b$pct_error),
  `95% CI` = sprintf("%.4f – %.4f", b$ci_low, b$ci_high),
  `Interval covers truth` = ifelse(b$covers_truth, "yes", "no"),
  check.names = FALSE))
```

```{r}
bp <- b
bp$estimator <- factor(bp$estimator, levels = rev(bp$estimator))
ggplot(bp, aes(x = estimate, y = estimator)) +
  geom_vline(xintercept = res$benchmark$truth$estimate, linetype = "dashed",
             colour = "#d95f02", linewidth = 0.7) +
  geom_errorbarh(aes(xmin = ci_low, xmax = ci_high), height = 0.12, linewidth = 0.6) +
  geom_point(aes(colour = covers_truth), size = 3) +
  scale_colour_manual(values = c("TRUE" = "#2c7fb8", "FALSE" = "#d7301f"), guide = "none") +
  labs(x = paste("Effect on", res$meta$outcome), y = NULL,
       caption = "Dashed line: true effect from the randomised data") +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank())
```

```{r}
#| output: asis
ov <- res$benchmark$overlap
cat(sprintf("**Common support: %s.** %s\n", ov$status, ov$message))
```

## Notes on interpretation

- An estimate is only as good as the assumption that identifies it. This report states which assumptions were checked and which failed.
- Where a validity check fails, the estimate is still shown but should not be treated as reliable without addressing the cause.
- Adjustment corrects for measured differences between groups. It cannot correct for anything that was not measured.